\subsection{Brennan Douglas}

    \subsubsection{Fall Week 3}
        
        \noindent
        Progress
        \begin{itemize}
            \item This week I learned what my project is and started communication with my team.  I learned the basics of what the project will be, and was given access to the pre existing code base.  When writing the problem statement I looked through my teammates notes of a previous meeting that they had already had with the sponsor to understand the basic requirements.  We also scheduled a weekly meeting for ourselves and with our TA as well.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item The only problems that I encountered this week were getting up to speed on what the project is/was as my teammates have already had a shoe in on this for awhile.  As they had met with the sponsor there was no need to rush that this week and therefore it will be a bit longer before I get a meeting with him.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item We plan to at this week’s meeting schedule the next meeting with our sponsor to get more detailed requirements laid out.  Also, we will begin to talk about how we will split work up, including how we will manage this.
        \end{itemize}
    
    \subsubsection{Fall Week 4}
    
        \noindent
        Progress
        \begin{itemize}
            \item This week I had my first personal team meeting with Joe, our advisor, over the phone.  We communicated about the requirements list that we had put together and clarified a few of the points.  We also have completed our group problem statement by splitting up the sections between ourselves and then each compiling a new section from our individual problem statements.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item No problems were encountered this week.  Everything week smoothly and was on time.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item We plan to have a team meeting early next week to write out some user stories to create a base for our requirements document.  From there we will  split up the work, using the previous team’s requirements document as reference for style.
        \end{itemize}
    
    \subsubsection{Fall Week 5}
    
        \noindent
        Progress
        \begin{itemize}
            \item This week our team had a few meetings to coordinate the requirements document and the tech review.  Our requirements document meetings were split into two parts: planning and revising.  We first decided on the outline for the document and then split up sections for us to individually complete.  Once we had all completed our sections we met again and smoothed them all together and revised our work.  From there we emailed it off to Joe, our advisor, and then submitted it.  We did the same breaking up for the start of our tech reviews; though we will not go through the revising phase as they are individual.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item There were no problems this week, all went smoothly.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item This upcoming week we all plan to work on and complete our tech reviews and submit them.
        \end{itemize}
        
    \subsubsection{Fall Week 6}
    
        \noindent
        Progress
        \begin{itemize}
            \item This week we finished our first draft of the requirements document.  We also had already split up and assigned all the sections for the tech review and thus were individually working on it.  I finished mine at the end of last week and let it sit for a bit before revising and submitting it.  We also needed to create a team standards document during Tuesday’s lecture.  We are all in agreement within terse terms for that as we are mainly following our work edicate (as we all work at the same software development job).
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item No problems occurred this week.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item This upcoming week we will be messing around with the code that already exists for our project to make sure that it is in a working conditions.  This will also have the effect of setting up all of our development environments.
        \end{itemize}
        
    \subsubsection{Fall Week 7}
    
        \noindent
        Progress
        \begin{itemize}
            \item This week I outlined, wrote, and turned in my first draft of the tech review.  Then in class we peer reviewed each other which meant I received actionable feedback that allowed me to revise and improve upon my draft.  After than carefully reading it over once more and making further changes I submitted the revised copy as my tech review final draft.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item I encountered no problems this week.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item Next week it appears that we will be starting to work on the design document (according to canvas).  I will be keeping an eye out for the requirements for this document as to begin to prepare for it.
        \end{itemize}
        
    \subsubsection{Fall Week 8}
    
        \noindent
        Progress
        \begin{itemize}
            \item This week our team laid out our first iteration of our development.  This only includes basic tasks like set up our development environments.  One big part of that was getting the development docker container for the API our application relies to work as expected.  So, this week I went through and wrote some dockerfiles and docker compose files to coordinate all the different services.  Along with this I also wrote some npm functions to ease the development process and act as an abstraction layer between us and docker when we are working so we don’t need to worry about any of the implementation details.  We also set up an outline for our design document.  We are each taking the sections that we worked on for the tech review and writing 500 words there.  For the introduction it is still generic enough that we were able to use the requirement documents description of our solution for this as well.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item Working with docker and environment variables can be really tricky and it took me quite a while to wade through all the little bugs that they caused.  Another issue is the previous code.  There is only fragmented documentation of what is what and where it is and, the repo wasn’t even fully up to date within its branches.  This caused me a fair amount of pain as I had some painful merges I had to do once we realized the most up to date code was not on the master branch.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item I have completed my task for the iteration (and more than the amount of hours that I am supposed to spend on this class) so I will be simply focusing on my portion of the design review.
        \end{itemize}
        
    \subsubsection{Fall Week 9}
    
        \noindent
        Progress
        \begin{itemize}
            \item This week I finished my section of the design document.  It was the database section, I mapped out the existing database into an ER diagram and discussed what needed to be changed to account for the new features and revisions.  I also started the progress summary document for my team along with a google slides instance which we will use when filming the video portion of the project summary.  The second half of the week... THANKSGIVING.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item There were no problems this week.  Even though most of the team was not in town for any useful portion of the week we are all effective at communicating remotely and were able to continue our work.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item We plan to film the video for the project summary Wednesday of week 10 (so next week).  This will give us plenty of time to edit it and upload it.  Along with plenty of time to complete our powerpoint slide over the weekend.
        \end{itemize}
        
    \subsubsection{Winter Week 1}
    
        \noindent
        Progress
        \begin{itemize}
            \item Just got back from winter break.  Our team did no work over winter break and just had a meeting to get back into the flow and assign initial tasks for implementation.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item There were no problems this week, not much was done.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item I will begin working on my tasks.  Also read up on what timelines we have this term (the early submission of the poster and elevator pitch).  I will focus on the database and dev-ops (docker) side of things.  An important first step is to get a script that adds test data to the database.
        \end{itemize}
        
    \subsubsection{Winter Week 2}
    
        \noindent
        Progress
        \begin{itemize}
            \item Decoded how the password is currently being hashed and salted.  Then created a script that runs inside of the API’s development docker container that adds a test admin user to the database if it does not already exist.  Also, the docker mechanism was simplified to only one dockerfile and using the standard docker-compose commands instead of the custom npm ones.  We also began discussing the design changes and how the data is supposed to fit together (not how the app is currently displaying it).
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item There were no problems this week.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item We will compile all of our specific design ideas and pass it by our advisor so that we can get approval to move forward.  In the meantime (for the backend --- the API) we are renaming some of the objects as they don’t fit with what they represent/what they are called in the user facing application.  I will also be looking into creating shadow tables for all of the main tables so that changes can be tracked.
        \end{itemize}
        
    \subsubsection{Winter Week 3}
    
        \noindent
        Progress
        \begin{itemize}
            \item We got the application converted over to typescript.  We got the login process working with test data as well as corrected it to make it more secure.  We also created the shadow tables for auditing in the database.  We haven’t created API routes yet but will when we need to.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item We found out that there are a whole lot of endpoints missing from the API that will have to be recreated.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item I am currently working to make the application homepage useable (at all).  This is an issue because of the missing endpoints.  I will then move the data entry form to the tank page so it can be added on a tank by tank basis.
        \end{itemize}
        
    \subsubsection{Winter Week 4}
    
        \noindent
        Progress
        \begin{itemize}
            \item I learned some of the basic lifestyle features of a vue page and moved the data entry component to the tank info page.  This involved passing the tank id that the data will be entered for as a prop to the component.  Refactoring of the page also started as we are rearranging the components to make more sense.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item The entire team is waiting for one task to be completed, that is for the API and app to be updated so that they work together as they weren’t out of the box.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item I will finish refactoring the tank info page and then remove the option on the data entry component for the recipe to be selected.  From there the batch interaction will be simplified as a new create batch component will be created and displayed when the tank is empty.
        \end{itemize}
        
    \subsubsection{Winter Week 5}
    
        \noindent
        Progress
        \begin{itemize}
            \item The API and the app are now compatible with each other and all the basic features of the application are now working.  We now aim to improve the application.  We started by adding a navbar so the pages can be easily moved between from any of them.  Also, now that my movement of the data entry component to the tank info page has been merged I’m starting to improve how the task/action functionality can improve.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item No problems currently.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item I will finish changing the batch submit process (on both the front-end and the back-end) so that the tasks are handled separately from the creation of the batch so that we can properly manage their life cycle.
        \end{itemize}
        
    \subsubsection{Winter Week 6}
    
        \noindent
        Progress
        \begin{itemize}
            \item This week I spent most of my time responding to code review comments from my teammates and resolving consistent errors on the application.  It was built in such a way that when a single page loaded multiple requests would be sent out to retrieve the same data (one for each component on the page).  These requests would mess with each others database connections on the API thus causes 500 errors to be returned.  By only getting the data once at the top level component, then the values can be passed down to each of the sub-components and they can do all their logic from those.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item No problems currently.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item I will begin to look into creating a complete batch button to allow for a batch to end its life cycle.  Along with that a new component for creating a batch will be made so that a batch life cycle can begin.  Once both of those are complete the application is to beta level functionality.
        \end{itemize}
        
    \subsubsection{Winter Week 7}
    
        \noindent
        Progress
        \begin{itemize}
            \item This week I refactored and simplified the update and create batch function.  Now it simply updates the batch with the new values and adds a new version associated with that batch.  I also added a complete batch button to complete the current batch on a tank.  Once confirmed it updates the data and shows the add batch component to the user (for the tank).
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item No problems currently.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item I still need to correct the colors on the homepage to work properly when there are expired tasks but no current ones.  Once this is done my changes can be merged in.  Then I will move onto extracting the actions from the update batch component as they are a live cycle of their own.
        \end{itemize}
        
    \subsubsection{Winter Week 8}
    
        \noindent
        Progress
        \begin{itemize}
            \item This week I simplified the tank-info page correcting its logic, adding a loader, and parallelizing its requests and tank model building.  Along with that I updated the look of the tank info boxes adding more proper formatting to them so they more easily display information now.  I needed to update the API to use a pool based database connection (the proper way) instead of what we were doing before to fix the parallel request 500 error that we have been seeing.  I also went through and updated the css to be mobile friendly with media queries while also removing all the mobile specific pages.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item No problems currently.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item I will be modularizing the tank status info from the tank-info page as that is the more proper vue form.
        \end{itemize}
        
    \subsubsection{Winter Week 9}
    
        \noindent
        Progress
        \begin{itemize}
            \item This week I didn’t accomplish too much past reviewing, changing, and merging in my changes from last week.  There were a lot of them so it took a fair amount of time.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item We seem to be at a standstill with unit testing.  We are having issues getting the unit testing framework loaded into the application.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item I will be debugging a recipe error where a newly submitted recipe with ingredients doesn’t display the ingredients.  I will also begin looking into the fermentation visualization graph.
        \end{itemize}
        
    \subsubsection{Winter Week 10}
    
        \noindent
        Progress
        \begin{itemize}
            \item This week I clarified the requirements for the fermentation curve with Joe at our weekly meeting.  I then created a python script to parse through the excel files of historical brewing data provided to us and mapped that into usable values for our application in the form of a csv.  Then I wrote an import script in TypeScript to parse and import all of the csv data into our application upon a post request.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item No problems.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item I will use these new test data to create the fermentation curve graph.
        \end{itemize}
        
    \subsubsection{Spring Week 1}
    
        \noindent
        Progress
        \begin{itemize}
            \item Spring break was great.  Meaning didn’t do anything.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item No problems.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item I will expand the fermentation curve graph to all the other graphs.
        \end{itemize}
        
    \subsubsection{Spring Week 2}
    
        \noindent
        Progress
        \begin{itemize}
            \item I added the history feature to the other of the three graphs on the two separate pages.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item No problems.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item Preparing the repo for the code freeze.
        \end{itemize}
        
    \subsubsection{Spring Week 3}
    
        \noindent
        Progress
        \begin{itemize}
            \item We submitted the code freeze url a little late as it was not clearly informed that this was necessary, but it is all complete now.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item Trying to figure out what to submit for revisions as we have none to make.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item Nothing, code is complete.  Just waiting on expo now.
        \end{itemize}
        
    \subsubsection{Spring Week 4}
    
        \noindent
        Progress
        \begin{itemize}
            \item Worked on revising the poster after first round of critiques came in.  Met with John Sweet to discuss possibilities and different options of selling out product.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item None.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item Nothing, code is complete.  Just waiting on expo now.
        \end{itemize}
        
    \subsubsection{Spring Week 5}
    
        \noindent
        Progress
        \begin{itemize}
            \item Got poster approved and sent for printing.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item None.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item Nothing, code is complete.  Just waiting on expo now.
        \end{itemize}
        
    \subsubsection{Spring Week 6}
    
        \noindent
        Progress
        \begin{itemize}
            \item Nothing has been happening.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item None.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item Nothing, code is complete.  Just waiting on expo now.
        \end{itemize}

\subsection{Dan Van Horn}
    \subsubsection{Fall Week 5}
        \noindent
        Progress
        \begin{itemize}
            \item This week we finalized our software requirements document and edited it again from Kirsten’s comments. We’ve sent the draft to our client. When we were assigned the tech review, we met and separated the project into different sections and assigned them amongst the group.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item There we’re no issues that we ran into this week.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item We’re going to work on the tech review this weekend and hopefully have some time for early development next week.
        \end{itemize}
    \subsubsection{Fall Week 6}
        \noindent
        Progress
        \begin{itemize}
            \item This week, we split up the possible technologies for our project and finished our tech reviews. We also turned in the requirements document. 
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item There we’re no issues this week because there wasn’t a lot of required work and we all finished the requirements document before the original due date.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item Next week we’ll be working on the next assigned document and finding some time to set up our development environment.
        \end{itemize}
    \subsubsection{Fall Week 7}
        \noindent
        Progress
        \begin{itemize}
            \item This week, we reviewed each other’s tech reviews, made the necessary edits, and turned in our final drafts.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item There were a lot of problems with our tech reviews that we ironed out amongst ourselves to make sure the final drafts were perfect.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item We’ve split up some research work and dev environment setup research work. This week we’ll meet and more formally define  the setup tasks that we need to do. 
        \end{itemize}
    \subsubsection{Fall Week 8}
        \noindent
        Progress
        \begin{itemize}
            \item This week we outlined the design document and assigned sections to each team member. We also started our project board and creates some tasks that were assigned. Individually, I started converting the backend API to typescript, and started adding continuous integration services like CircleCI.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item One problem that occurred was that the original tests that were written for the project are integration tests, not unit tests, so they will not integrate into our continuous integration process. This is fine, but we will have to write unit tests in the meantime.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item We will continue to work on our sections of the design document and continue with some preliminary development. 
        \end{itemize}
    \subsubsection{Fall Week 9}
        \noindent
        Progress
        \begin{itemize}
            \item I completed the front-end portion of the design document and created some diagrams to explain front-end data flow and the architecture of the whole project. I also worked on the portions of the progress update slideshow that I researched.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item There were no problems this week. Although I didn’t get to work on the typescript conversion of the API this week because of Thanksgiving. 
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item Next week we’ve allocated time to finish the design document and the progress report on Wednesday. We’ll also continue to work on the tasks that we are assigned on our GitHub project board.
        \end{itemize}
    \subsubsection{Winter Week 1}
        \noindent
        Progress
        \begin{itemize}
            \item We had a team meeting this week to discuss the development that we'd like to finish before next week. We also contacted out client to set up bi-weekly progress report meetings.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item There weren't any technical or administrative problems this week.

        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item Our plan is to complete all of the issues that are on our project board for the current sprint. Next Wednesday we'll create more tasks based on our Gandtt chart from last term.
        \end{itemize}
    \subsubsection{Winter Week 2}
        \noindent
        Progress
        \begin{itemize}
            \item We've had another team meeting this week to talk about the changes that we're going to be making to our front end app. We had a meeting with our client to update him on our progress. I've been developing new feature for the API that will make the front end changes much easier.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item I had some technical problems with the API not handling HTTP requests correctly and had to do a large refactor on the project. This has blocked me from inserting test data to be used on the front end but I will finish that today.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item We're going to work on front end re-design changes and have another meeting with our client next Tuesday.
        \end{itemize}
    \subsubsection{Winter Week 3}
        \noindent
        Progress
        \begin{itemize}
            \item This week, we were able to add test data into the database and run the front-end app and API together. We also cleared up some questions that we had during our client meeting and confirmed some tasks that we were going to perform.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item The requests that are defined in the app do not match with those defined in the API so we will have to painstakingly refactor both projects so that we are expecting the right data and routes.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item The request incompatibility between the API and app is the highest priority task in the coming week. We're also going to be adding a new page and re-arranging some visual components of the app.
        \end{itemize}
    \subsubsection{Winter Week 4}
        \noindent
        Progress
        \begin{itemize}
            \item This week we finished making the API and app requests compatible with each other. We also added a navbar component to that makes it way easier to use. We've also made some other structural changes to the front end that we're requested by our client.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item The biggest problem this week was scheduling a time to meet for the poster review that would work for everyone. We have a problem updating batches of beer with new actions.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item We're going to continue to make front end changes that were requested by the client. We'll need to clarify some Ninkasi-specific actions with the client.
        \end{itemize}
    \subsubsection{Winter Week 5}
        \noindent
        Progress
        \begin{itemize}
            \item This week we completed a lot of UI changes that made the app much easier to navigate. We also got some confirmation for additional UI elements that we wanted to run by our client.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item Some of our UI changes broke mobile compatibility so we'll need to fix those. We did find a bug in the application but it was a nice one-line fix.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item We have a lot of pull requests to review which is great because that means we have a lot of code that was added this week. Once those are reviewed an merged in, we'll have to add an additional UI component for creating new batches of beer in a tank.
        \end{itemize}
    \subsubsection{Winter Week 6}
        \noindent
        Progress
        \begin{itemize}
            \item This week I added a new component to create a new batch and begin the batch lifecycle. We received some feedback regarding our color coding of batch actions. We also worked on our progress report draft.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item Our client feedback would require changes throughout our whole stack so we'll have to clarify what they actually want.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item We plan to finish our progress report by Monday. We will have a meeting with our client to nail down batch actions. We plan to complete the logic for going through an entire batch lifecycle.
        \end{itemize}
    \subsubsection{Winter Week 7}
        \noindent
        Progress
        \begin{itemize}
            \item This week I was able to get continuous deployment set and the app hosted on heroku. We were also able to complete the lifecycle of a batch opening and closing them which is one of the key features that was not operational from the previous year.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item Some bugs revealed themselves that we'll have to fix in the coming week. Mostly on the front end.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item The client requested some more changes to the app. This time they will not require change throughout the whole stack. We'll focus, in the coming week, on the clients specific requests. 
        \end{itemize}
    \subsubsection{Winter Week 8}
        \noindent
        Progress
        \begin{itemize}
            \item This week we fixed some bugs that revealed themselves during deployment. We finished implementing some changes that our client that requested. Some of the changes required changes throughout the whole stack but they we're easier than originally expected.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item We had deployment and database issues that required a lot of debugging and redeploying the application. Luckily we were able to figure these issues out.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item We're going to make sure that we can deplete the lifecycle of a batch and try to root out any additional bugs, especially in regards to different user levels.
        \end{itemize}
    \subsubsection{Winter Week 9}
        \noindent
        Progress
        \begin{itemize}
            \item This week, we planned for our progress report video and I made some bug fix changes to the app.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item There weren't any problems this week.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item We've delegated the remaining work to get the app to beta level functionality to the team members and will then shift the focus to testing the app.
        \end{itemize}
    \subsubsection{Winter Week 10}
        \noindent
        Progress
        \begin{itemize}
            \item I made a lot of changes to the admin page and gave admins more control over tanks, users and brands. We also filmed our progress report video and submitted the final progress report.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item There were no problems this week.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item We'll be focusing more on testing in the coming weeks and editing the progress video.
        \end{itemize}
    \subsubsection{Spring Week 1}
        \noindent
        Progress
        \begin{itemize}
            \item Finished testing on the API and got very acceptable code coverage. Merged our dev branch into master and redeployed the app.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item No problems this week.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item The plan for me next week is to implement testing on the front end and making sure we are tracking the user's id with each request that needs it.
        \end{itemize}
    \subsubsection{Spring Week 2}
        \noindent
        Progress
        \begin{itemize}
            \item This week I made sure we are correctly handling user ids throughout the app. 
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item I was unable to get testing running on the front end. I would need more time and the code freeze is coming up.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item This week I'll be reviewing the final PRs and making any changes to our github documentation.
        \end{itemize}
    \subsubsection{Spring Week 3}
        \noindent
        Progress
        \begin{itemize}
            \item The code freeze was this week so we merged all of our code to the master branch. We also reviewed our docs and determined that we don’t need to make any changes to the requirements.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item We didn't have any problems this week. We didn't know we had to turn in a link to our master repo on the due date but we haven't pushed any additional code and I think many other groups did that as well.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item Next week we'll address any additional assignments and due dates.
        \end{itemize}
    \subsubsection{Spring Week 4}
        \noindent
        Progress
        \begin{itemize}
            \item This week we talked about the future of our project as far as IP goes and we finished our poster. We also started on a business plan.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item This week went smoothly.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item We will continue to work on the business plan and keep our eyes open for the next capstone responsibilities we have to take care of.
        \end{itemize}
    \subsubsection{Spring Week 5}
        \noindent
        Progress
        \begin{itemize}
            \item We worked on our business plan, and edited our poster for the final submission.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item There were no issues this week.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item Keep our eyes open for additional due dates and capstone responsibilities.
        \end{itemize}
    \subsubsection{Spring Week 6}
        \noindent
        Progress
        \begin{itemize}
            \item This week we didn't have anything to do except for get ready for expo. We know where our table is.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item There were no issues this week as we didn't have to develop or write any documents.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item Next week we'll have to attend expo and give our client the estimated cost for the project.
        \end{itemize}




\subsection{Henry Peterson}
    \subsubsection{Fall Week 4}
        \noindent
        My group and I finished our problem statement with out issue. We also had a phone meeting with our client and met with our TA. We plan to meet on monday to discuss and work on the requirements document. No problems have arisen so far.
    \subsubsection{Fall Week 5}
        \noindent
        This week, we finalized our draft for the requirements documents and decided on who would write about what for the tech review. Next week I will write about my section of the tech review and work on the next draft of the requirements document. We have had no issues so far. 
    \subsubsection{Fall Week 6}
        \noindent
        This week we finished writing our tech reviews.
        This was a relatively slow week in terms of group work so we encountered no problems.
        In the future, we will revise our drafts of the tech review based on the feed back. We may meet with our client soon, but we may cancel that as we do not have much to discuss.
    \subsubsection{Fall Week 7}
        \noindent
        This week I revised my tech review into a final draft and met with our TA.
        It was a relatively light week so no problems were encountered.
        Next week, we will work on our requirements document.
    \subsubsection{Fall Week 8}
        \noindent
        This week, as a group we made plans for the design document and the update video.
        We met with the TA, had a fine discussion, and ran into no issues.
        Our plan is to finish the design document after the week 9 break.
    \subsubsection{Fall Week 9}
        \noindent
        This week was the week of thanksgiving. I actually did nothing whatsoever for this class this week. I did not talk to my group either. But we still have our plans to work on and finish the design document and video next week, no one should be unsure of what is going on.
    \subsubsection{Winter Week 1}
        \noindent
        This week we met with our client, Joe, and had a brief discussion about our plans coming up. Little was actually done, mostly just gaining our bearings coming off winter break.
        No problems so far.
        We plan to start implementing types on both the front and back ends of the application. Some updates to the database should occur as well.
    \subsubsection{Winter Week 2}
        \noindent
        On my area, the front end, we got typescript implemented. No actual types, everything is 'any' type, but type checking is occurring.
        No big problems. We need to find a good place to host our website for testing.
        Next we will convert the 'any' types to actual usable types.
    \subsubsection{Winter Week 3}
        \noindent
        The vast majority of the 'any' types have been converted to usable types. In our weekly meetings with Joe, we've had more discussion and clarification on what exactly needs to change with the user interface.
        No problems. If any, it just been unforeseen refactors that need to be made.
        Next steps are to implement changes to the UI including making the tank monitoring clearer and putting data entry on its own page.
    \subsubsection{Winter Week 4}
        \noindent
        This week I updated the batch history page and created the tank history page. This included improving the csv printing functionality and the overall css. I also had to add an API route to retrieve batches by tank.
        The only problem this week was the poster critique scheduling being a pain in the rear.
        Next week we will show our design changes for Joe to consider and then change them based on that again.
    \subsubsection{Winter Week 5}
        \noindent
        this week I fixed batch history styles/types as well did some refactoring to make charts appear nicely on the page.
        No problems yet.
        next steps will be adding action history to batch history 
    \subsubsection{Winter Week 6}
        \noindent
        This week I looked into testing.
        Testing is a lot tougher to implement that I expected.
        Next week I will add task history tables.
    \subsubsection{Winter Week 7}
        \noindent
        This week I added task history tables and refactored how some charts are displayed.
        No problems this week.
        Next I will fix how CSVs are formatted and work on mobile compatibility.
    \subsubsection{Winter Week 8}
        \noindent
        This week I did not get as much done as I had hoped to due to responsibilities in other classes and at work, so I guess that was my biggest issue with this week.
        What I did get done was almost completing reorganizing the downloaded CSV to be how the client would like it.
        Hopefully testing framework will be implemented soon ;(
    \subsubsection{Winter Week 9}
        \noindent
        This week I refactored the tank info component and finished up the csv download feature.
        The biggest problem right now is getting the testing framework together.
        The plan is to look into the csv upload feature next.
    \subsubsection{Winter Week 10}
        \noindent
        This week I added a CSV upload to the tank entry page.
        No problems so far.
        Next I will work on batch selection issues.
    \subsubsection{Spring Week 1}
        \noindent
        This week we met with the client and got back up to speed after spring break. we've had no issues so far. Next week, I will work on editing the data entry component. 
    \subsubsection{Spring Week 2}
        \noindent
        Week I moved data entry to the tank monitoring page. I ran into an issue with finishing batches, but I know how to fix it. we also updated the documentation for running the program. 
    \subsubsection{Spring Week 3}
        \noindent
        This week I worked on implementing the updated csv upload. It is not complete and I will continue it. We also met with John Sweet about the product.
        There have been no problems.
        Next week I will work on the batch completion update as well.
    \subsubsection{Spring Week 4}
        \noindent
        This week I polished up the bulk upload feature and worked on the updated batch completion.
        I hope to finish that next week.
    \subsubsection{Spring Week 5}
        \noindent
        This week I did not do much.
        I did not finish the update batch feature, but It not required for a bit.
        The foreseeable plan is to prepare for expo and ensure all of out materials are together.
    \subsubsection{Spring Week 6}
        \noindent
        This week has been spent preparing for expo.
        No problems have arisen.
        
\subsection{Bailey Singleton}
        
    \subsubsection{Fall Week 4}
        \noindent
        Progress
        \begin{itemize}
            \item
            We met with out TA, Mariam. We also finalized out problem statement doc and turned it in. We talked to our client and they seemed thrilled out about the problem statement.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item
            No problems here. All is good.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item
            We will make our requirements doc for week 5, and it is going to be great.
        \end{itemize}

    \subsubsection{Fall Week 5}
        \noindent
        Progress
        \begin{itemize}
            \item
            We finished up our requirements doc and got it in. Communicated with client, all is well
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item
            No problems as of now, things are going smoothly.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item
            Technical review doc is next on the agenda.
        \end{itemize}
    \subsubsection{Fall Week 6}
        \noindent
        Progress
        \begin{itemize}
            \item
            Finished up my tech review which went pretty well, no major problems
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item
            No issues to report, overall painless week. 
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item
            I am going to start revising my tech review this week. 
        \end{itemize}
    \subsubsection{Fall Week 7}
        \noindent
        Progress
        \begin{itemize}
            \item
            Finished up my Tech Review, so I feel good on that. I think it turned out well.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item
            No problems this week!
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item
            I plan to work on getting our build environment set up and keeping up with the intensive documentation.
        \end{itemize}
    \subsubsection{Fall Week 8}
        \noindent
        Progress
        \begin{itemize}
            \item Discussed what we were going to work on for the presentation video. 
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item No problems on much this week.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item We plan on getting started on our video. 
        \end{itemize}
    \subsubsection{Fall Week 9}
        \noindent
        Progress
        \begin{itemize}
            \item Started working on design document with group, and enjoying some thanksgiving.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item No problems so far, other than I haven't eaten any turkey yet.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item Plan to work on the presentation video next week, after finishing the design doc.
        \end{itemize}
    \subsubsection{Winter Week 1}
        \noindent
        Progress
        \begin{itemize}
            \item Met with team, divided up initial tasks. Got in touch with client and set up a bi-weekly meeting.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item No problems to report.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item We plan to start working on our initial goals this weekend, through next week.
        \end{itemize}
    \subsubsection{Winter Week 2}
        \noindent
        Progress
        \begin{itemize}
            \item Continued to work on typescript conversion, met with our TA and chatted. 
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item None to report.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item Finish typescript conversion, and move onto testing. 
        \end{itemize}
    \subsubsection{Winter Week 3}
        \noindent
        Progress
        \begin{itemize}
            \item Finished typescript conversion, and met with our client.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item No problems yet
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item Working on refactoring the front end this week into next. Moving tank data entry to the data page.
        \end{itemize}
    \subsubsection{Winter Week 4}
        \noindent
        Progress
        \begin{itemize}
            \item  Made a navbar this week for the webapp. Looks pretty slick.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item Finding a group and meeting time for poster critique that works for everyone has been a major pain.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item Meet with other group to do poster critique. Make some cool login changes.
        \end{itemize}
    \subsubsection{Winter Week 5}
        \noindent
        Progress
        \begin{itemize}
            \item Finished cleaning up some Navbar changes, now working on login fixes.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item None to report. 
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item Continue working on login functionality, and the rough draft of report. 
        \end{itemize}
    \subsubsection{Winter Week 6}
        \noindent
        Progress
        \begin{itemize}
            \item Got some more information from our client on certain colors they are looking for to indicate certain actions.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item None so far
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item Work on tweaking some navbar fixes.
        \end{itemize}
    \subsubsection{Winter Week 7}
        \noindent
        Progress
        \begin{itemize}
            \item Made some navbar fixes, also corrected an issue in the login process.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item  None to report this week.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item  Continue to polish front end, and implement some suggestions brought to our attention by our client.
        \end{itemize}
    \subsubsection{Winter Week 8}
        \noindent
        Progress
        \begin{itemize}
            \item Fixed mobile compatibility, and added in a date picker to the project. 
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item None really.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item Work on final video, and make the slides. 
        \end{itemize}
    \subsubsection{Winter Week 9}
        \noindent
        Progress
        \begin{itemize}
            \item Fixed up mobile compatibility on tank history page. Outlined our progress video final.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item Ran into a problem in my PR review, need to fix up an issue when the app is used on a screen of 300 pixels wide.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item  Fix the mobile compatibility issues, and also film the final progress video.
        \end{itemize}
    \subsubsection{Winter Week 10}
        No progress report made.
    \subsubsection{Spring Week 1}
        \noindent
        Progress
        \begin{itemize}
            \item  Recorded winter progress video, fixed up our progress report. 
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item No problems this week.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item Edit progress video and submit it.
        \end{itemize}
    \subsubsection{Spring Week 1}
        \noindent
        Progress
        \begin{itemize}
            \item No new progress, coming back from spring break. Preparing for code freeze with teammates
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item No problems, smooth going.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item Finish up a few bugs before code freeze. Mostly scrolling fixes which should be easy.
        \end{itemize}
    \subsubsection{Spring Week 2}
        \noindent
        Progress
        \begin{itemize}
            \item Fixed CSS bugs with scrollbars
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item None to report. 
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item Prep for code freeze. Iron out last bugs 
        \end{itemize}
    \subsubsection{Spring Week 3}
        \noindent
        Progress
        \begin{itemize}
            \item Turned in all code for code freeze. 
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item None to report! All is good. 
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item Do write up for guest speaker. 
        \end{itemize}
    \subsubsection{Spring Week 4}
        \noindent
        Progress
        \begin{itemize}
            \item Re submitted our poster for final review. 
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item None
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item Get ready for expo.
        \end{itemize}
    \subsubsection{Spring Week 5}
        \noindent
        Progress
        \begin{itemize}
            \item Submitted poster.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item Not much.
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item Prepare my body and soul for expo.
        \end{itemize}
    \subsubsection{Spring Week 6}
        \noindent
        Progress
        \begin{itemize}
            \item Went to class on Friday to prepare for Expo.
        \end{itemize}
        
        \noindent
        Problems
        \begin{itemize}
            \item No problems to report!
        \end{itemize}
        
        \noindent
        Plans
        \begin{itemize}
            \item Prepare for Expo.
        \end{itemize}
