\subsubsection{Fall}
\hfill\break
\noindent\medskip\textbf{Week 1}
Updated resume and got peer feedback.
Submitted project preferences.
Setup OneNote and modeled structure after Kevin's email.

\noindent\medskip\textbf{Week 2}
Worked on individual problem statement.

\noindent\medskip\textbf{Week 3}
Met with Daniel Sharp on Wednesday at Ninkasi Brewing Company.

\noindent\medskip\textbf{Week 4}
Met with Connor and Lily on Wednesday to hash out the problem statement. We go the metrics figured out, they will need to be revised as we get more details from Daniel.
We completed out Problem Statement and uploaded the documents to GitHub and the Group 10 OneNote.
Lily is sending Daniel an email to check in, get access to the master spreadsheet which the database will be based on, ask him if he'd like access to the GitHub, and figure out a good time for us to come visit again.

\noindent\medskip\textbf{Week 5}
Wrote rough draft Requirements Document with Lily and Connor. Set up next phone meeting with Daniel Sharp (client) on Wednesday at 5.

\noindent\medskip\textbf{Week 6}
This week we finalized our Special Requirements Specifications document.
Lily, Connor, and I hashed out the necessary details that will allow us to develop a working system that will solve our client, Daniel Sharp's, needs.
Daniel was unable to give us feedback on our document until 6pm Friday, and so Kirsten gave our group an extension until Monday night.
We also came up with a name for our team, BrewHops.
Now, we are beginning to look at the technical review.
Overall, I think we got important stuff done this week.

\noindent\medskip\textbf{Week 7}
Got our requirements document approved and submitted.

\noindent\medskip\textbf{Week 8}
Completed rough draft of the Tech Review.
Doing additional research on hardware hosts.
As of now, it looks like Raspberry Pi could be a good prototype, but not super viable long-term as its I/O speeds could not support heavy database traffic.
Another option is Intel NUCs which have much better I/O speeds but also cost a lot more.
Can also create Docker container to virtualize on personal computer for now if we do not want to worry about getting hardware for this project.

\noindent\medskip\textbf{Week 9}
Submitted final draft of the technology.
Scheduled meeting with Daniel Sharp for Dec 1.

\noindent\medskip\textbf{Week 10}
Met with Oregon Brewers Association today to discuss how other breweries are tackling these issues.


\subsubsection{Winter}
\hfill\break
\noindent\medskip\textbf{Week 1}
Established weekly meeting time with Connor and Lily.

\noindent\medskip\textbf{Week 2}
Met with Connor and Lily on Thursday to discuss GitHub issues and how we want to incorporate AGILE into our development cycle.

\noindent\medskip\textbf{Week 3}
Met with Connor and Lily on Thursday for our weekly catchup.
Initialized GitHub repository for the server-side code.
Modified Ruby and Rails versions and specified dependencies.
Also, generated the \`Employee\` model and began learning how the Ruby on Rails framework works.

\noindent\medskip\textbf{Week 4}
Generated the \`Employees\` controller to work with the \`Employees\` database model.
Exposed URL endpoint for the \`Employees\` model.
Met with Connor and Lily for weekly catchup.

\noindent\medskip\textbf{Week 5}
Began messing around with Heroku as a hosting system and deployment method.
Generated the \`Action\` and \`Recipe\` model and created controllers for both.

\noindent\medskip\textbf{Week 6}
Added basic validation of attributes at the Rails level to \`Employee\`, \`Action\`, and \`Recipe\` models.
Met with Connor and Lily to figure out what information they needed me to pull back from the database at each endpoint.
Created the \`Tanks\` model and controller.
Began working on poster with Lily and Connor.
Created the midterm progress report with Lily and Connor.

\noindent\medskip\textbf{Week 7}
Figured out how to add foreign keys at the database level for necessary tables.
Also, reworked the ER diagram to a normalized schema.
Built the \`Batches\` model and controller.
Added in the referential integrity at the database level using foreign keys.

\noindent\medskip\textbf{Week 8}
Created the \`Batch\_Contents\_Version\` model to store daily values from the fermentation tanks.
Had a work session with Connor and Lily.

\noindent\medskip\textbf{Week 9}
Added in mock data for existing application instance on Heroku.
Met with Lily and Connor to discuss the frontend.

\noindent\medskip\textbf{Week 10}
Built out the \`Tasks\` model and controller.
Finalized all database attributes and ensure referential integrity of tables at both the database and rails levels.
Had a work session with Lily and Connor to complete the final demo and video progress report.
Completed personal progress report.

\subsubsection{Spring}
\hfill\break
\noindent\medskip\textbf{Week 1}
Met with Connor and Lily to discuss everything left to complete on the project.
Added more routes to the backend.

\noindent\medskip\textbf{Week 2}
Made minor fixes to the database structure.
This included a few name changes and datatype changes.

\noindent\medskip\textbf{Week 3}
Drove down to Eugene with Connor and Lily to present our final product to Ninkasi.
Daniel Sharp and his team were present for the presentation.
They agreed to begin beta testing the application for us the following week.

\noindent\medskip\textbf{Week 4}
Modified the api structure so that data was aggregated on the server side.
This prevented the client application from making numerous network calls to the server.

\noindent\medskip\textbf{Week 5}
Finished some content for the poster.

\noindent\medskip\textbf{Week 6}
Connor let Daniel Sharp know that our application was ready for beta testing.

\noindent\medskip\textbf{Week 7}
Presented project at the Engineering Exposition.

\noindent\medskip\textbf{Week 8}
No work completed this week.

\noindent\medskip\textbf{Week 9}
No work completed this week.

\noindent\medskip\textbf{Week 10}
Completed assigned tasks for the final progress report.
